Scaling Automated Theory Exploration

### 2015-08-06 AI4FM/article.tex
Reworded

Automated theory exploration has been applied to libraries in Isabelle
and Haskell, although we focus on the latter as its implementations are
the most mature (demonstrated by the fact that \textsc{Hipster} explores
Isabelle by first translating it to Haskell). Haskell is interesting to target,
since its use of pure functions and algebraic datatypes causes many functions to
follow algebraic laws. However, since Haskell's type system cannot encode such
laws (without difficulty \cite{lindley2014hasochism}, at least); less
effort is given to finding and stating them, compared to a theorem proving
setting like Isabelle. Hence, Haskell provides much low-hanging fruit for a
broad but shallow exploration to discover.

>>>>

Automated theory exploration has been applied to libraries in Isabelle
and Haskell, although we focus on the latter as its implementations are
the most mature (demonstrated by the fact that \textsc{Hipster} explores
Isabelle by first translating it to Haskell). Haskell is interesting to target,
since its use of pure functions and algebraic datatypes causes many programs to
follow algebraic laws. However, since Haskell's type system cannot easily
encode such laws, less effort is given to finding and stating them; compared to
a theorem proving setting like Isabelle.
